\title{An Analyzer for ANSI C}
\author{D. J. Banta\\
D. L. Carroll\\
S. A. Maurich\\
J. R. Roccatagliata\\
P. A. Shanahan\\
C. R. Turner\\
W. M. Waite}
\maketitle

This document assumes familiarity with the basic principles of compiler
construction and access to the Eli documentation.
It is made up of a collection of FunnelWeb files, one per chapter.

The actual specification is embedded in the text as macros, sequentially
numbered within each chapter.
A macro is a relevant chunk of the specification, with a name describing
its purpose.
It may have references to other macros as components.
Our intent is that the names of the referenced macros carry sufficient
information to make the chunk itself understandable.

Attached to each macro definition is the set of macro numbers in which it
is used, and attached to each use is the macro number of its definition.
This allows the reader to easily find more information about a component
if necessary.
Some macro definitions are broken up to allow insertion of explanatory text.
In this case, each section of the definition is given a distinct sequential
number and all of them are attached both to each definition and to each use.

This specification, originally developed as a class project in the spring
semester of 1994, implements ANSI/ISO 9899-1990.
Within the document, ANSI/ISO 9899-1990 is referred to as ``the standard''.

The specification was tested using Eli 4.5.
A complete description of Eli, including the current public-domain source
code, can be found on the
\htmladdnormallinkfoot{web}{http://www.cs.colorado.edu/~eliuser/}.

\newpage

\tableofcontents
